\sysfull

### 2017-10-30 paper/paper.tex
Covering Koen's comments
conclusions compressed
Bacground compressed
stash pop merge
\newpage removed
made article style PLDI complaint

%\documentclass[sigconf,anonymous,review]{acmart}
\documentclass[pageno]{jpaper}

@@

\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm} % environment for the algorithm code (like figure and table)
\usepackage{algorithmicx} % write the pseudo code
\usepackage[noend]{algpseudocode} % layout of the pseudo code
\usepackage{tikz} % needed for: tikz pics
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{tikz}
\usepackage{listings}
%Brandon: this broke the build for me
%\usepackage[keeplastbox]{flushend}

\hypersetup{colorlinks=false,linkcolor=blue,urlcolor=blue}
\urlstyle{rm}

@@

%Title Options (Brandon: your call which one)
%\newcommand{\sysfull}{VIPER: Virtualised Intermittent Programming model, Execution model, and Runtime environment}
%\newcommand{\sysfull}{VIPER: Virtualized Intermittently-Powered Execution Runtime}
%\newcommand{\sysfull}{PREVIEW: Programming and Runtime Environment with Virtualised Intermittent Execution Windows}
%\newcommand{\sysfull}{VIPE: Virtualized Intermittently-Powered Execution}
\newcommand{\sysfull}{\sys: Efficient Task-based Intermittent Execution with Adaptive Coalescing and Memory Virtualization}

@@

\section{\sysfull}
\label{sec:overall_system}

@@

\section{Discussion}
\label{sec:discussion}

\input{discussion}

@@

\section{Conclusions and Future Work}
\label{sec:conclusions}

@@

\newpage

>>>>

%\documentclass[sigconf,anonymous,review]{acmart}
%\documentclass[pageno]{jpaper}
\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm} % environment for the algorithm code (like figure and table)
\usepackage{algorithmicx} % write the pseudo code
\usepackage[noend]{algpseudocode} % layout of the pseudo code
\usepackage{tikz} % needed for: tikz pics
\usepackage{xcolor}
\usepackage{xspace}
%\usepackage{tikz}
\usepackage{listings}
%\usepackage{float}
%Brandon: this broke the build for me
%\usepackage[keeplastbox]{flushend}

%%Added for sub-float package from jpaper.cls - will check later

\RequirePackage[font={normalsize,sf,bf}]{caption}
\RequirePackage[position=bottom]{subfig}
\captionsetup[table]{aboveskip=0.5em, belowskip=0.5em}
\captionsetup[figure]{aboveskip=0.5em, belowskip=0em}
\captionsetup[subfloat]{font={small,sf}}

\hypersetup{colorlinks=false,linkcolor=blue,urlcolor=blue}
\urlstyle{rm}
\linespread{0.98}

\newlength{\sectionbelowskip}
\newlength{\sectionaboveskip}
\newlength{\subsectionbelowskip}
\newlength{\subsectionaboveskip}
\newlength{\paragraphaboveskip}

% Defaults in sigplanconf (note that horizontal space after \paragraph heading will be different):
%\setlength{\sectionbelowskip}{4pt}
%\setlength{\sectionaboveskip}{10pt plus 3pt minus 2pt}
%\setlength{\subsectionbelowskip}{4pt}
%\setlength{\subsectionaboveskip}{8pt plus 2pt minus 2pt}
%\setlength{\paragraphaboveskip}{6pt plus 2pt minus 2pt}

% Slightly tighter than defaults:
% \setlength{\sectionbelowskip}{3pt}
% \setlength{\sectionaboveskip}{6pt plus 2pt minus 2pt}
% \setlength{\subsectionbelowskip}{2pt}
% \setlength{\subsectionaboveskip}{4pt plus 1pt minus 1pt}
% \setlength{\paragraphaboveskip}{2pt plus 1pt minus 1pt}

% Tighter than defaults:
 \setlength{\sectionbelowskip}{1pt}
 \setlength{\sectionaboveskip}{5pt plus 1.5pt minus 1.5pt}
 \setlength{\subsectionbelowskip}{1pt}
 \setlength{\subsectionaboveskip}{3pt plus 1pt minus 1pt}
 \setlength{\paragraphaboveskip}{1pt plus 1pt minus 1pt}

@@

%Title Options (Brandon: your call which one)
%\newcommand{\sysfull}{VIPER: Virtualised Intermittent Programming model, Execution model, and Runtime environment}
%\newcommand{\sysfull}{VIPER: Virtualized Intermittently-Powered Execution Runtime}
%\newcommand{\sysfull}{PREVIEW: Programming and Runtime Environment with Virtualised Intermittent Execution Windows}
%\newcommand{\sysfull}{VIPE: Virtualized Intermittently-Powered Execution}
\newcommand{\sysfull}{\sys: Efficient Task-based Intermittent Computing with Adaptive Task Coalescing and Memory Virtualization}

@@

\section{\sys: System Overview}
\label{sec:overall_system}

@@

%\section{Discussion}
%\label{sec:discussion}

%\input{discussion}

@@

\section{Conclusions}
\label{sec:conclusions}

@@

%\newpage
